Listings of equations, figures, tables and sections of the article '{\it \bf Musical elements in the discrete-time representation of sound}' and of the scripts in the MASS toolbox

### 2017-08-05 article/acm/listings.tex
finished the listings

\subsection{In Section 4 - Notes in music}

\subsection{In Section 3 - Variations of the basic note}
\subsection{In Section 4 - Notes in music}

\clearpage
\section{Figures}

@@

\clearpage
\section{Scripts}
\subsection{For all equations in each chapter}
\clearpage
\subsection{To render musical pieces}
\clearpage
\subsection{To render the figures used in the article}

\clearpage
\section{Other documents}
Latex files. PDF files.
MSc Dissertation.

\section{Final considerations}

>>>>

\clearpage
\section{Figures}\label{sec:lfigures}

\begin{table*}[htp!]
\centering
\caption{Figure numbers and their descriptions.
All these equations are implemented in files \texttt{src/aux/*}.}
\begin{tabular}{ c | p{12cm} }
   Number & Description \\\hline
 \ref{fig:PCM} & PCM PCM audio (discrete and digital) samples \\
 \ref{fig:formasDeOnda} & synthetic and sampled waveforms \\
 \ref{fig:espectroDeOndas} & spectrum of basic waveforms \\
 \ref{fig:espectroOboe} & spectrum of a real note and of one derived from one sampled period \\
 \ref{fig:amostras2} & sinusoid represented by two samples \\
 \ref{fig:amostras3} & sinusoid represented by three samples \\
 \ref{fig:amostras4} & sinusoids in 4 samples \\
 \ref{fig:formas4} & basic waveforms within 4 samples \\
 \ref{fig:amostras6} & sinusoids in 6 samples \\
 \ref{fig:formas6} & basic waveforms withing 6 samples \\
 \ref{fig:spac} & ITD and IID (spatial localization cues)\\
 \ref{fig:mixagem} & mixing PCM audio \\
 \ref{fig:concatenacao} & concatenation/juxtaposition of PCM audio \\
 \ref{fig:lut} & Lookup table \\
 \ref{fig:transicao} & transitions of intensity \\
 \ref{fig:conv} & convolution \\
 \ref{fig:delays} & convolution yielding time shifting, multiple time delays, sound amalgam \\
 \ref{fig:iir} & frequency response of useful IIR filters \\
 \ref{fig:ruidos} & spectrum and waveform of noises \\
 \ref{fig:vibrato} & spectrogram of a vibrato \\
 \ref{fig:tremolo} & waveform of a tremolo \\
 \ref{fig:adsr} & ADSR envelope \\
 \ref{fig:movContraponto} & counterpoint movements \\
 \ref{fig:pulsoSubAgl} & musical metric in terms of divisions of temporal units \\
 \ref{fig:climax} & distinctions of musical climax by localization \\
\end{tabular}
\end{table*}

@@

\begin{table*}[htp!]
\centering
\caption{Table numbers and their descriptions.}
\begin{tabular}{ c | p{12cm} }
   Number & Description \\\hline
 \ref{eq:intervalos} & musical intervals, their notations and qualities \\
 \ref{tab:harmonia} & tonal harmonic functions in the major scale \\
 \ref{tab:duracoes} & duration scales yielding perception of pitch and rhythm \\
 \ref{tab:change} & music by permutation of units (change ringing) \\
\end{tabular}
\end{table*}

\clearpage
\section{Scripts}
\subsection{For all equations and relations in each section.}

\begin{table*}[htp!]
\centering
\caption{Script files and their descriptions.}
\begin{tabular}{ c | p{12cm} }
   Filename & Description \\\hline
  \texttt{src/sections/2.py} & implementation of all the equations for the basic note in PCM audio in Section~\ref{sec:discNote} \\
  \texttt{src/sections/3.py} & implementation of all the equations for variations within a note described in Section~\ref{sec:varInternas} \\
  \texttt{src/sections/4.py} & implementation of all the techniques for assembling notes into music described in Section~\ref{sec:notesMusic} \\
\end{tabular}
\end{table*}

\clearpage
\subsection{To render musical pieces}

\begin{table*}[htp!]
\centering
\caption{Piece names, script files and the concepts they exemplify from Section~\ref{sec:discNote}. All files are in the directory \texttt{src/pieces2/}.}
\begin{tabular}{ p{5cm} | p{3.5cm} | p{6.2cm} }
   Name & Filename & Description \\\hline
 Reduced-fi & \texttt{reduced-fi.py} & concatenation of simple notes \\
 Sonic pictures & \texttt{quadrosSonoros.py} & mixing of simple notes  \\
\end{tabular}
\end{table*}

\begin{table*}[htp!]
\centering
\caption{Piece names, script files and the concepts they exemplify from Section~\ref{sec:internalVar}. All files are in the directory \texttt{src/pieces3/}.}
\begin{tabular}{ p{5cm} | p{3.5cm} | p{6.2cm} }
   Name & Filename & Description \\\hline
 ADa and SaRah & \texttt{ADAandSaRah.py} & ADSR envelope \\
 Tremolos, Vibratos and Frequency & \texttt{bonds.py} & bonds between tremolos, vibratos and frequency  \\
 Bella Rugosi & \texttt{bellaRugosi.py} & rugosity achieved through frequencies between 15 adn 30 Hz \\
 Children Choir & \texttt{childChoir.py} & achieving choir sonorities by small variations of the same basic note \\
 Noisy Band & \texttt{noisyBanda.py} & using various noises \\
 ParaMeter Transitions & \texttt{paraMeter.py} & gradual changes of parameters within one note \\
 Little Train of Impulsive Hillbilies~\footnote{This names translates into ``Trenzinho de Caipiras Impulsivos'' which is a pun with the Villa-Lobos' ``Trenzinho do Capira''.} & \texttt{littleTrain.py} & the use of convolution with impulses to achieve rhythm \\
 Shakes and Wiggles & \texttt{shakesWiggles.py} &  tremolos and vibratos \\
\end{tabular}
\end{table*}

\begin{table*}[htp!]
\centering
\caption{Piece names, script files and the concepts they exemplify from Section~\ref{sec:notesMusic}. All files are in the directory \texttt{src/pieces4/}.}
\begin{tabular}{ p{5cm} | p{3.5cm} | p{6.2cm} }
   Name & Filename & Description \\\hline
 Acorde Cedo & \texttt{acordeCedo.py} & chord successions and modulation \\
 Conta Ponto & \texttt{contaPonto.py} & melodic lines conducted within the rules of counterpoint \\
 Crystals & \texttt{crystals.py} & symmetric musical scales \\
 Dirracional & \texttt{dirracional.py} & directional arcs \\
 Intervals & \texttt{intervals.py} & musical intervals \\
 MicroTone & \texttt{microTone.py} & microtonality (the use of intervals smaller than the semitone) \\
 Poly-Hit-My & \texttt{polyHitMy.py} & polyrhythm (multiple metrics at once) \\
\end{tabular}
\end{table*}

\clearpage
\subsection{To render the figures used in the article}
The files \texttt{src/figures/*} render each of the figures (listed above in Section~\ref{sec:lfigures}.

\clearpage
\section{Other documents}
The files in \texttt{latex/*} render the article PDF and this Supporting Information file.

The script \texttt{src/aux/iso226.py} can generate the Equal Loudness Contour as described in its latest revision~\cite{iso226}.

The article is largely based on the MSc dissertation~\cite{dissertacao}.
